---
title: "Homework1"
author: Jyoti Kumar
output: github_document
---

This is my R Markdown File for Homework1

```{r}
library(tidyverse)
```


## Problem 1

## Creating a data frame

```{r create_df}
prob1_df =  
   tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low","low","low","mod", "mod", "mod", "mod", "high", "high", "high")),
    )
```

 Taking the mean of each variable in the data frame.

```{r mean_pull_variables}
mean(pull(prob1_df,samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

 We can take the mean of numbers and logical terms but not of characters and factors. 

```{r conversion_to_numeric}
as.numeric(pull(prob1_df,samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```


```{r}
as.numeric(pull(prob1_df,samp_gt_0)) * pull(prob1_df,samp)
(pull(prob1_df, factor_vec)) * pull(prob1_df, samp)
as.numeric(pull(prob1_df, factor_vec)) * pull(prob1_df, samp)
```

 We can multiply numeric data with the random sample but not factors.


## Problem 2


```{r}
data( "penguins", package = "palmerpenguins")
```

```{r}
summary(penguins)
```


## The data set includes the palmer penguins dataset includes the following:
The species and the island they are from, the bill length and depth in mm, the flipper length in mm, body mass, sex and their year.
The data has `r nrow(palmerpenguins::penguins)` rows and
The data has `r ncol(palmerpenguins::penguins)` columns.
The mean flipper length is 200.9 mm

# Plotting bill_length_mm vs flipper_length_mm

```{r}
library(tidyverse)
penguins_df = tibble(
  x = (penguins$bill_length_mm),
  y = (penguins$flipper_length_mm),
  z = (penguins$species)
)
ggplot(penguins_df, aes(x = x, y = y, color = z)) + geom_point()
ggsave("scatter_plot.pdf")
```



 





